Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/structureScene.tex
cleaning outputs

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity, researchers have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13b}. 
In addition, recent work has explored acoustic monitoring for characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound}, as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these applications are of considerable interest for the signal processing community.

@@

A support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets \cite{cortes-vapnik}. From another point of view, it attemts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have rendered SVMs a popular choice for many classification systems.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{bw/folds.png}
\caption{\label{fig:folds}
Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies.  Performance on each fold is depicted using a given symbol.
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.}
\end{center}
\end{figure}

@@

As shown in Figure \ref{fig:folds}, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.
This is in accordance with previous results on similarity retrieval, as well as comparisons between mel-frequency coefficients and scattering coefficients for tasks ranging from musical genre recognition and phone segment classification \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/anden}}]{Joakim And\'en}
received the M.Sc. degree in mathematics from the Universit\'e Pierre et Marie Curie, Paris, France, in 2010 and the Ph.D. degree in applied mathematics from Ecole Polytechnique, Palaiseau, France, in 2014. He is currently a postdoctoral researcher with the Program in Applied and Computational mathematics at Princeton University, Princeton, USA. His research interests include signal processing, machine learning, and statistical data analysis. He is a member of the IEEE.

@@

\begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his Ph.D. in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, TELECOM ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
\end{IEEEbiography}

>>>>

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity researchers have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13b}. 
In addition, recent work has explored acoustic monitoring for characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound}, as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these applications are of considerable interest for the signal processing community.

@@

A support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets \cite{Cortes1995}. From another point of view, it attemts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have rendered SVMs a popular choice for many classification systems.

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=\columnwidth]{bw/folds.png}
%\caption{\label{fig:folds}
%Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies.  Performance on each fold is depicted using a given symbol.
%The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
%The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.}
%\end{center}
%\end{figure}

@@

%As shown in Figure \ref{fig:folds}, scattering coefficients outperform MFCCs over all but one fold of the DCASE 2013 private dataset when applying early integration, and over all folds when applying late integration.

As shown on Table \ref{table:dcase2013}, scattering coefficients outperform MFCCs on the DCASE 2013 private dataset when applying early and integration.
This is in accordance with previous results on similarity retrieval, as well as comparisons between mel-frequency coefficients and scattering coefficients for tasks ranging from musical genre recognition and phone segment classification \cite{Anden2014} to environmental sound classification \cite{Salamon2015}.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/anden}}]{Joakim And\'en}
received the M.Sc. degree in mathematics from the Universit\'e Pierre et Marie Curie, Paris, France, in 2010 and the PhD degree in applied mathematics from Ecole Polytechnique, Palaiseau, France, in 2014. He is currently a postdoctoral researcher with the Program in Applied and Computational mathematics at Princeton University, Princeton, USA. His research interests include signal processing, machine learning, and statistical data analysis. He is a member of the IEEE.

@@

\begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his PhD in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, TELECOM ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
\end{IEEEbiography}
